Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-28 doc/ecp/pres.tex
Final draft.
Fixed spelling error.

  Investigate use in time-dependent applications, e.g. fluid flow, compustion,
  non-linear radiation hydrodynamics for high-energy density physics
  applications:
  \vfill
  \begin{itemize}
  \item Used as inner linear solver in a non-linear (Newton) iteration
  \vfill
  \item Time-dependent applications generally have strong diagonal-dominance
    that makes MCSA competitive with Krylov methods
  \vfill
  \item MCSA has resiliency and parallel efficiency benefits over conventional
    subspace methods
  \end{itemize}

@@

  A supporting technolgies research effort on a generalized set of libraries
  for managing particle-based data structures on heterogeneous computing
  platforms will benefit many applications in DOE

@@

@@

>>>>

  Apply MCLS to time-dependent applications, e.g. fluid flow, compustion,
  non-linear radiation hydrodynamics for high-energy density physics
  applications:
  \vfill
  \begin{itemize}
  \item Used as inner linear solver in a non-linear (Newton) iteration
  \vfill
  \item Time-dependent applications generally have strong diagonal-dominance
    that makes MCSA competitive with Krylov methods
  \vfill
  \item MCSA has resiliency and parallel efficiency benefits over conventional
    subspace methods
  \end{itemize}

@@

  A supporting technologies research effort on a generalized set of libraries
  for managing particle-based data structures on heterogeneous computing
  platforms will benefit many applications in DOE

@@

%%---------------------------------------------------------------------------%%
\subsection{ECP Roadmap}
%%---------------------------------------------------------------------------%%

\begin{frame}{A Monte Carlo and Particle Methods Roadmap for ECP}

  \centering
  \includegraphics[width=1\textwidth]{timeline}

@@

\begin{frame}
\vfill
\centering
\huge Extra Slides
\vfill
\end{frame}
